\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage{fontspec}
\usepackage{xeCJK}
\usepackage[colorlinks=true,urlcolor=blue,linkcolor=blue]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}

\setmainfont{Times New Roman}
\setCJKmainfont{Songti SC}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\hyphenpenalty=10000
\exhyphenpenalty=10000
\emergencystretch=2em
\setlist[itemize]{leftmargin=1.6em,itemsep=2pt,topsep=2pt}
\titleformat{\section}{\large\bfseries}{}{0pt}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{5pt}

\newcommand{\entry}[4]{
  \textbf{#1} \hfill #2\\
  \textit{#3}\\
  #4
}

\newcommand{\smallentry}[3]{
  \textbf{#1} \hfill #2\\
  \textit{#3}
}

\begin{document}

\begin{center}
  {\LARGE\bfseries HONGJI CHEN {\large 陈鸿基}}\\[6pt]
  (+86) 139-2266-9419 $\diamond$
  \href{mailto:hongjichen25@m.fudan.edu.cn}{hongjichen25@m.fudan.edu.cn} $\diamond$
  \href{https://realzillionx.github.io/}{Website} $\diamond$
  \href{https://github.com/realZillionX}{GitHub} $\diamond$
  \href{https://scholar.google.com/citations?user=N7Ytb68AAAAJ&hl=en}{Google Scholar}
\end{center}

\section*{Education}
\smallentry{Fudan University, Shanghai}{Sept. 2025 -- Present}
{Undergraduate Student}

\vspace{3pt}
\smallentry{Shanghai Innovation Institute and Fudan University, Shanghai}{Starting Fall 2029}
{Incoming Ph.D. Student, advised by Prof. Xipeng Qiu}

\section*{Honors and Awards}
\begin{itemize}
  \item Shanghai Innovation Institute Ph.D. Offer, Summer 2026
  \item Youngest SII Ph.D. offer recipient up to Summer 2026
\end{itemize}

\section*{Research Interests}
Multimodal reasoning, AI infrastructure, UMM (Unified Multimodal Models), VGM (Video Generation Models), and WAM (World Action Model).

\section*{Publication}
\begin{itemize}
  \item \textbf{AI Can Learn Scientific Taste}\\
  Jingqi Tong, Mingzhe Li, Hangcheng Li, Yongzhuo Yang, Yurong Mou, Weijie Ma, Zhiheng Xi,
  \textbf{Hongji Chen}, Xiaoran Liu, Qinyuan Cheng, Ming Zhang, Qiguang Chen, Weifeng Ge,
  Qipeng Guo, Tianlei Ying, Tianxiang Sun, Yining Zheng, Xinchi Chen, Jun Zhao, Ning Ding,
  Xuanjing Huang, Yugang Jiang, Xipeng Qiu. \textit{arXiv preprint arXiv:2603.14473}, 2026.
\end{itemize}

\section*{Experiences}
\smallentry{Shanghai Innovation Institute}{Jul. 2026 -- Present}
{Research Intern, advised by Prof. Xipeng Qiu}

\vspace{5pt}
\smallentry{Fudan NLP Lab / OpenMOSS Team}{Oct. 2025 -- Present}
{Research Intern, advised by Prof. Xipeng Qiu}

\section*{Selected Projects}
\entry{Shanghai Innovation Institute Research Cockpit}{2026 -- Present}
{Major participant}
{Full-process agentic research operating system for organized research, upgrading AI from stage-specific assistance to automated literature search, idea generation and evaluation, research-plan generation from goals, execution tracking, iterative verification, and lifecycle management. \href{https://github.com/realZillionX/InspireSkill}{InspireSkill} is a concrete outcome of this project, providing reusable skills and tool interfaces for agents to operate the Inspire compute platform through reproducible workflows.}

\section*{Skills}
\textbf{Programming:} Python, C/C++, Bash, Git, \LaTeX\\
\textbf{Frameworks and Tools:} PyTorch, Hugging Face Transformers, Linux, agent workflow infrastructure\\
\textbf{Research:} UMM (Unified Multimodal Models), VGM (Video Generation Models), WAM (World Action Model), AI research systems

\end{document}
